Estimating duration in the presence of misclassification

### 2024-01-25 transmission.tex
Start notes on comparison

>>>>

Comparing the regional incidence estimates between the two models in this chapter.

Example of bias---variance trade-off.

Demonstrated by fitting to the North East.
Quality of fit in SEIR model is variable between different age groups.
This is because the model is not flexible enough to capture the true age distribution of infections.
